

# Dziennik modeli

```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

require(gt)

dziennik <- data.frame(Model=sort(rep(c('EWS', 'Debt Sales','Recovery', 'OCR_One_Pager', 'Wolumeny CKK'),3)), Wersja = rep(c('v.0.1','v.0.2','v.0.3'),5), Autor = rep(c('Lukasz Muszynski', 'Krzysztof Dylus', 'Andrzej Olszyna'), 5), Zlecone_przez = rep(c('CKD', 'CKD','CKD','CAWK', 'CAWK','CAWK','CKK', 'CKK','CKK','CAWK', 'CAWK','CAWK','CAWK', 'CAWK','CAWK')), Data_wdrozenia = rep(c('2020-01-01'), 15), Data_wycofania = rep(c('2020-03-01'), 15), Zagadnienie=c('klasyfikacja binarna', 'klasyfikacja binarna', 'klasyfikacja binarna','klasyfikacja binarna', 'klasyfikacja binarna', 'klasyfikacja binarna','OCR PDF-ow', 'OCR PDF-ow', 'OCR PDF-ow','klasyfikacja binarna', 'klasyfikacja binarna', 'klasyfikacja binarna','szereg czasowy','szereg czasowy','szereg czasowy'), Deployment = c('Server modelowy (Python)', 'Server modelowy (Python)', 'Server modelowy (Python)', 'Server modelowy (Python)', 'Server modelowy (Python)', 'Server modelowy (Python)','IWA','IWA','IWA', 'Server modelowy (Python)', 'Server modelowy (Python)', 'Server modelowy (Python)', 'Server modelowy (Python)', 'Server modelowy (Python)', 'Server modelowy (Python)'), Link_PL=rep(c('...'),15), Link_EN=rep(c('...'),15) ) 



dziennik %>%
  gt(rowname_col = "Wersja", groupname_col = "Model") %>%
  tab_spanner(label = "Dates and Times", columns = matches("date|time")) %>%
  tab_header(
    title = md("Dziennik modeli"),
  ) %>%   cols_width(
    starts_with("Depl") ~ px(200),
    starts_with("Link_PL") ~ px(300)
  )


```



# Modele



## DEBT SALES

### v.0.1 PL

Karta modelu
<br><br>
```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
require(tibble)

require(kableExtra)


library(dplyr)
library(knitr)
library(kableExtra)
require(gr)
require(gtable)
library(gridExtra)

knit_table <- function(df){

    df %>%
      kable("html", escape = F) %>%
      kable_styling()
}


t <- tribble(
  ~Kategoria, ~Wartość,
  "Zagadnienie", "Klasyfikacja binarna",
  "Metoda",   'RandomForest',
  "parametry",   'n_estimator=100, max_depth=5',
  "target", "0-odzysk w ciągu 12 miesięcy < 20% \n1-odzysk w ciągu 12 miesięcy <= 20%",
  "features", '(1) CB - salbo cd na date badania \n(2) max_DPD - max dpd z 12 miesiacy przed badaniem \n(3) opłaty - suma oplat na 6 miesiecy przed badaniem \n(4) kontakt_2Q - czy kontakt klient w ciagu 2 kwartalow przed badaniem',
  "zbiór treningowy", "120000, (2019-10-01:2020-01-01)",
  "zbiór walidacyjny", "40000, (2019-10-01:2020-01-01)",
  "zbiór testowy", "50000, (2020-01-01:2020-05-01)",
  "punkt odcięcia", "0.3",
  "Accuracy", "0.85",
  "Balanced accuracy", '0.75',
  "Recall", "0.65",
  "Precision", "0.83",
  "Uwagi", "(1) Problem nie zbalansowania klas \n(2) niska liczebność próby"
)


tt3 <- ttheme_default(core=list(fg_params=list(hjust=0, x=0.1)),
                      rowhead=list(fg_params=list(hjust=0,x=0.1)))

grid.table(t, theme = tt3, rows = NULL)


```


##### Wstęp

###### Cel biznesowy
###### Narzędzie i źródła danych
###### Architektura modelu


#### Analiz zmiennych
##### Metodyka
##### Zmienna 1
##### Zmienna 2
##### Zmienna 3
##### Zmienna 4
##### Korelacje zmiennnych

#### Budowa modelu
##### Budowa zbiorów
##### Metodyka
##### Wyniki



### v.0.1 EN

### v.0.2 PL

### v.0.2 EN

### v.0.3 PL

### v.0.3 EN



## EWS

### v.0.1 PL

### v.0.1 EN

### v.0.2 PL

### v.0.2 EN

### v.0.3 PL

### v.0.3 EN


## OCR ONE PAGER

### v.0.1 PL

### v.0.1 EN

### v.0.2 PL

### v.0.2 EN

### v.0.3 PL

### v.0.3 EN


## RECOVERY

### v.0.1 PL

### v.0.1 EN

### v.0.2 PL

### v.0.2 EN

### v.0.3 PL

### v.0.3 EN


## WOLUMENY CKK

### v.0.1 PL

### v.0.1 EN

### v.0.2 PL

### v.0.2 EN

### v.0.3 PL

### v.0.3 EN





# Data Science book

## Metody nadzorowane
### Regresja
#### liniowa
#### logistyczna
### Ensambled models
#### Random Forest
#### Gradient Boost
### Szeregi czasowe
#### ARIMA
#### Średnia ruchoma
#### GARCH
### Sieci nauronowe
#### Sieci proste
#### CNN
#### Sieci rekurencyjne


## Metody nienadzorowane
### k-means
### DBSCAN
### Mieszanki GAussowskie


## Miary
### Korelacje
### Regresja
### Klasyfikacja


## Data preprocessing
### Imputacja danych
### Wartości odstające
### Encoding
### Preprocessing obrazu
### Preprocessing dzwięku
### Preprocessing tekstu
### Redukcja wymiaru



